From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-07-29 WOLFHPC15/article/mscac.tex
fix compiler 29_07

\begin{figure*}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (D) at (0,0) {Driver};
   \node[provide] (Dp) at (-1,0) {};
   \node (Ds) at (-1.5,0) {start};
   \node[use] (Du1) at (1,0.5) {};
   \node[use] (Du2) at (1,-0.5) {};

   \node[component,right=1cm of Du2] (DA) {DriverApp};
   \node[use] (DAu1) at (3.5,0) {$m$};
   \node[use] (DAu2) at (3.5,-1) {};

   \node[component] (T) at (4.5,-1) {Time};
   \node[use,right=1cm of T] (Tu) {};
   \node[component,right=2cm of Tu] (C) {Computations};
   \node[use,right=2cm of C] (Cu) {};
   \node[below=0.2cm of Cu] (star) {$*$};

   \node[component,right=8cm of DAu1] (Data) {Data};
   \node[use,right=1cm of Data] (Datau) {};

   \node[component,right=13cm of Du1] (DDS) {DDS};

>>>>

\begin{figure*}
\begin{center}
\begin{tikzpicture}[shorten >=1pt, node distance=2cm, on grid, auto]
   \node[component] (D) at (0,0) {$Driver$};
   \node[provide] (Dp) at (-1,0) {};
   \node (Ds) at (-1.5,0) {start};
   \node[use] (Du1) at (1,0.5) {};
   \node[use] (Du2) at (1,-0.5) {};

   \node[component,right=1cm of Du2] (DA) {$DriverApp$};
   \node[use] (DAu1) at (3.5,0) {$m$};
   \node[use] (DAu2) at (3.5,-1) {};

   \node[component] (T) at (4.5,-1) {$Time$};
   \node[use,right=1cm of T] (Tu) {};
   \node[component,right=2cm of Tu] (C) {$Computations$};
   \node[use,right=2cm of C] (Cu) {};
   \node[below=0.2cm of Cu] (star) {$*$};

   \node[component,right=8cm of DAu1] (Data) {$Data$};
   \node[use,right=1cm of Data] (Datau) {};

   \node[component,right=13cm of Du1] (DDS) {$DDS$};
